%% start of file 'John-Van-Note-Resume.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%%
%% John Van Note
%% 2016-01-09
%%
%% My resume source code
%%

% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\documentclass[10pt,a4paper,sans]{moderncv}

% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{classic}

% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{blue}

% to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}

% uncomment to suppress automatic page numbering for CVs longer than one page
\nopagenumbers{}

% character encoding
% if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[utf8]{inputenc}

% if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
%\usepackage{CJKutf8

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% if you want to change the width     of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}
% for the 'classic' style, if you     want to force the width allocated to your name and avoid line breaks. be careful thou    gh, the length is normally calculated to avoid any overlap with your personal info; u    se this at your own typographical risks...
%\setlength{\makecvtitlenamewidth}{10cm}

% personal data
\name{John}{Van Note}
% optional, remove / comment the line if not wanted
%\title{Resumé title}
\address{6210 Belcrest Road, Apt. 1438}{Hyattsville, MD}{20782}
\phone[mobile]{215.518.0823}
\email{johnlvannote@gmail.com}
\homepage{https://github.com/JohnVanNote}

\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Experience}
\cventry{Feb. 2016 to Current}{Software Support Engineer}{Corporation Service Company}{Wilmington, DE}{}{
    \textit{Technologies used: Java, Groovy, Python, BASH, Apache HTTP Server, Apache Tomcat 7, IIS 7/8, Oracle Weblogic 12c, Oracle 11g, GitHub, VirtualBox.}%
    \begin{itemize}%
        \item Developed a solution to remediate application server slownesss issues using a custom Python library I developed to execute BASH commands on Apache Tomcat server.
        \item Engineered and supported the implementation of an enterprise ETL tool across four environments, spanning more than twelve application servers.
        \item Designed and developed a Groovy application to generate an automated application performance index report on a monthly basis. This report aggregated data from multiple reporting tools including using the Splunk SDK and reading from and Oracle 11G database backend.
        \item Engineered and implemented production Business Intelligence Reporting tool.
        \item Developed fine-grain procedures for upgrading enterprise Capture and Process management using ned Oracle E-Business Suite backend.
\end{itemize}}

\cventry{Mar. 2015 to Feb. 2016}{Technical Application Support Engineer}{Corporation Service Company}{Wilmington, DE}{}{
    \textit{Technologies used: Groovy, VBA, BASH, Splunk, GitHub, SVN, Apache Tomcat, IIS, Oracle 11g.}%
    \begin{itemize}%
        \item Automated monthly reporting using VBA to parse data and generate charts in Microsoft Excel.
        \item Individually maintained a legacy Grails Application, fixing application bugs and extending functionality.
        \item First responder and level one support for over 10 applications including: Apache Tomcat instances and IIS servers.
\end{itemize}}

\cventry{Oct. 2014 to Jan. 2015}{Technical Support Engineer}{Solve Media, Inc.}{Philadelphia, PA}{}{
    \textit{Technologies used: JavaScript, VBA, Perl, PHP, Python, Ruby, Java, .NET, VyprVPN, VMWare Fusion.}%
    \begin{itemize}%
        \item Provided technical support of external customers integrating open-source CAPTCHA technology in a variety of languages/frameworks including Perl, PHP, Python, Ruby, JSP (Java), and ASP.NET. This also included supporting plugins for various open-source content management systems, such as WordPress.
        \item Used JavaScript and VBA to automate a process estimating customer availability across geographic targets reducing, overall estimation time by over 80\% and improving reliability.
        \item Completed code reviews and quality assurance tasks on existing libraries and plug-ins.
\end{itemize}}


\section{Education}
\cventry{Sept. 2008 to Jun. 2013}{Bachelor of Science in Business Administration, Minor in Computer Science}{Drexel University}{Philadelphia, PA}{\textit{3.59 GPA}}{}

\section{Computer skills}
\cvlistitem{Programming/Scripting Languages: Python, Java/Groovy, C/C++, BASH/Shell, JavaScript, VBA, Ruby.}
\cvlistitem{Technologies: GitHub, VirtualBox, IntelliJ, iTerm2, SVN.}
\cvlistitem{Servers: Apache HTTP Server, IIS 7/8, Apache Tomcat 7, Oracle WebLogic 12c.}
\cvlistitem{Operating Systems: RedHat Linux, OSX, Windows 2012 R2.}
\cvlistitem{Database: Oracle 11g.}

\section{Honors}
\cvlistitem{Eight-time Drexel Univeristy Dean’s List recipient}
\cvlistitem{A.J. Drexel Scholarship recipient, 2008 to 2013}

\end{document}
%% end of file 'John-Van-Note-Resume.tex'.
