%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{John}{Van Note}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{6210 Belcrest Road, Apt 1438}{Hyattsville, MD}{20782}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{215.518.0823}                   % optional, remove / comment the line if not wanted
\email{johnlvannote@gmail.com.}                               % optional, remove / comment the line if not wanted
\homepage{https://github.com/JohnVanNote}                         % optional, remove / comment the line if not wanted
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2008 to 2013}{BS in Business Administration, Minor in Computer Science}{Drexel University}{Philadelphia, PA}{\textit{3.59 GPA}}{}

\section{Experience}
\cventry{February 2016 to Current}{Application Technologies Engineer}{Corporation Service Company}{Wilmington, DE}{}{
Responsibilities:%
\begin{itemize}%
\item Building and upgrading enterprise applications on both the Windows and Unix operating systems across multiple environments maintaining stability and scailability while adhering to tight-defined schedules.
\item Supporting various cross-functional applications by resolving server-side issues and making configuration changes necessary for a growing environment.
\item Creating and implementing architecture plans to leverage existing technologies to solve new organizational needs.
\end{itemize}}

\cventry{March 2015 to February 2016}{Technical Application Support Engineer}{Corporation Service Company}{Wilmington, DE}{}{
Responsibilities:%
\begin{itemize}%
\item Improved team productivity by automating a series of reporting tasks using Java/Groovy and Visual Basic For Applications.
\item Primary support representative for over 10 in-house and third-party applications.
\item Responded to customer technical application issues in a timely fashion maintained responsibility for issue resolution.
\end{itemize}}

\cventry{October 2014 to January 2015}{Technical Support Engineer}{Solve Media, Inc.}{Philadelphia, PA}{}{
Responsibilities:%
\begin{itemize}%
\item Guided publishers through technical implementation of open-source client-side and server-side code.
\item Created automation scripts to estimate customer availability across geographic targets reducing overall estimation time by over 50\%.
\item Assisted with code review and quality assurance.
\end{itemize}}

\section{Computer skills}
\cvlistitem{Programming/Scripting Languages: Python, C++, Java, Groovy, BASH, JavaScript, VBA.}
\cvlistitem{Technologies: GitHub, VirtualBox, IntelliJ, iTerm2, SVN.}

\section{Honors}
\cvlistitem{Kofax Capture \& Extraction for MarkView 8 Certification}
\cvlistitem{Eight-time Drexel Univeristy Dean’s List recipient}
\cvlistitem{A.J. Drexel Scholarship recipient, 2008 to 2013}

\clearpage
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Mapbox}{}
\date{September 15, 2016}
\opening{Dear Sir or Madam,}
\closing{Sincerely,}

\makelettertitle

I am writing this in response to the Support Engineer position at Mapbox. There a several reasons why I am interested position, not the least of which is the responsibilities of the position itself. The description of the position places an emphasis on the breadth of the position, including responsibilities like developing, writing, and working with customers. Personally, I have always found positions with a wide range of activities more rewarding and, generally, help me develop faster, both professionally and as an individual. I will likely always lean to the position which is more development heavy, but I will have always have an interest in other responsibilities.

I have limited exposure to the mapbox platform at this time. I stumbled onto this website during a routine job search, but this position caught my eye. I have taken the time to review your Mapbox GL JS library as well as the, widly impressive, Mapbox Command line interface I found on github (which as a sidenote, inspired me to begin a project refactoring an old command line utility I wrote as an exercise in college using the click package, which, in its beginning stages, can be found here: https://github.com/JohnVanNote/cd-flatfile-database/tree/click). While my exposure is limited, what interests me in Mapbox as a potential place of employment is the technology. I am fascinated by the opportunity of working in the fast pace of an open source tech company and hope to absorb some of the technical expertise.

I feel my greatest value to the position, more so than my technical backround, would be my customer facing roles. From October 2014 until late January 2015 I worked as a Technical Support Engineer for Solve Media, Inc., where the focus of my work was responding to customer inqueries about technical implementation of the product. As Solve Media provided opensource libraries to customers which they could use to implement CAPTCHA TYPE-IN ads on their own website, I feel the experience is comparable. Upon leaving my position, I was lucky to receive recommendations from both my direct superior as well as CIO, which can be found on my LinkedIn profile.

I feel my current position is comparable to the Support Engineer position, as I work as a member of the infrastruture team with a focus in operations since March 2015. In this case my \"customers\" tend to be developers within the same organization. Despite the increase technical proficiency of a developer, there is still a high level of empathy that needs to be taken when giving support, as the divide leaves many unfamiliar with the processes and procedures at the infrastructure level. At this position I have also received formal written praise, although it is internal.

The Technical Support opportunity at Mapbox seems to be an intersection where my experience and my interest collide. The thing that interests me most about the position is the ability to learn. The products I have seen are truely impressive and I hope that I can contribute in a meaningful way.

My resume is included. I appreciate the consideration; please feel free to contact me at your earliest convenience.

\makeletterclosing

\end{document}

%% end of file `resume.tex'.
